---
title: "Analysis co-bidding networks"
author: "Camila Salazar"
date: "8/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data cleaning

The datasets used for the analysis are availale here:

```{r message=FALSE, warning=FALSE, error=FALSE}
  setwd("/Users/camilasalazar/Documents/LSE/Capstone Project/data")
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(ggthemes)
library(knitr)
library(kableExtra)
library(readxl)

options(scipen=999)
#Read datasets
adj <- read_csv("final datasets/adj.csv", col_types = cols(X1 = col_skip()))
load("bidders_dataset_full.Rdata")
winners_full<-readRDS("winners_full2.Rdata")
rate <- read_excel("final datasets/rate.xlsx")
bidders_info <- read_csv("final datasets/bidders_info.csv")
load("sub_market.Rdata")
load("market_full.Rdata")
market_final<-readRDS("market_final.Rdata")


type<-adj%>%
  select(id, tipo_procedimiento_codigo, tipo_procedimiento, institution2, nombre_licitacion, categoria, year, monto_total_adjudicado, moneda, fecha_publicacion)%>%
  mutate(procedure=ifelse(tipo_procedimiento_codigo %in% c("CO", "LC", "LPI", "LPN"), "open", "closed"))%>%
  select(-categoria)%>%
  left_join(rate, by="year")%>%
  mutate(amount_dolar=ifelse(moneda=="Guaraníes", monto_total_adjudicado/rate, monto_total_adjudicado))

#Clean bidders dataset
bidders_dataset <- bidders_dataset%>%
  #Delete duplicates
  distinct()%>%
  #Create a column about the number of bidders per contract
  group_by(con)%>%
  mutate(total_bid=n())%>%
  #Add columns about the type of procedure
  left_join(type, by= c("con" = "id"))

#Translate names of markets
market_final<-market_final%>%
  mutate(marketf=ifelse(marketf=="Alimentos Bebidas y Tabaco", "Food, beverages and tobacco",
                 ifelse(marketf=="Computadoras","Computers",
                  ifelse(marketf=="Equipo informatico y accesorios", "Computer equiment and accessories",
                  ifelse(marketf=="Equipos Accesorios y Suministros Medicos", "Medical equipment",
                  ifelse(marketf=="Equipos y Suministros de limpieza", "Cleaning equipment",
                  ifelse(marketf=="Fontaneria, calefaccion y aire acondicionado", "Plumbing, heating and air conditioning",
                  ifelse(marketf=="Instalacion, mantenimiento y reparacion de energia electrica y aparatos eléctricos", "Installation, maintenance and repair of electrical appliances",
                  ifelse(marketf=="Instrumentos de medida, observacion y ensayo", "Lab equipment",
                  ifelse(marketf=="Medicamentos y Productos Farmaceuticos", "Medical and pharmaceutical products",
                  ifelse(marketf=="Muebles", "Furniture",
                  ifelse(marketf=="Neumaticos y camaras de neumaticos", "Tires",
                  ifelse(marketf=="Papel de imprenta y papel de escribir", "Paper",
                  ifelse(marketf=="Pavimentación,construccion, arreglo o hermoseamiento de carreteras o caminos", "Pavement",
                 ifelse(marketf=="Ropas, Maletas y Productos de Aseo Personal", "Clothes, luggage and personal care products",
                  ifelse(marketf=="Seguro de vehiculos", "Vehicle insurance",
                  ifelse(marketf=="Seguros de edificios o del contenido de edificios", "Building insurance",
                  ifelse(marketf=="Servicios de guardias de seguridad", "Security guards services",
                  ifelse(marketf=="Servicios de limpieza de edificios", "Cleaning services",
                  ifelse(marketf=="Servicios de reparacion, mantenimiento de transportes", "Vehicle repair and maintenance",
                  ifelse(marketf=="Suministros de oficina", "Office supplies",
                  ifelse(marketf=="Suministros para impresora, fax y fotocopiadora","Supplies for printer, fax and photocopier",
                   ifelse(marketf=="Viajes en aviones comerciales", "Airplane travel", 
                   ifelse(marketf=="Restauracion y/o reparacion de edificios, mojones o monumentos", "Restauracion y reparacion de edificios, mojones o monumentos", 
                  ifelse(marketf=="Turismos / Especiales", "Turismos Especiales", 
                  ifelse(marketf=="Vehiculos Comerciales, Militares y Particulares - Accesorios y Componentes", "Vehiculos Comerciales, Militares y Particulares Accesorios y Componentes", marketf))))))))))))))))))))))))))
```

## Descriptive results for the full market

```{r message=FALSE, warning=FALSE, error=FALSE}
#Proportion of open tenders
tenders<-bidders_dataset%>%
  group_by(con)%>%
  mutate(row=row_number())%>%
  filter(row==1)%>%
  select(con, total_bid)%>%
  left_join(type, by=c("con"="id"))

kable(round(prop.table(table(tenders$procedure))*100, 2))%>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")

#Summary statistics and distribution of the number of bidders
summary(tenders$total_bid[tenders$procedure=="open"])

tenders%>%
  filter(procedure=="open")%>%
  ggplot(aes(x=total_bid))+
  geom_histogram()+
  theme_minimal()+
  scale_x_continuous("Number of bids")+
  scale_y_continuous("Number of firms")+
  ggtitle("Plot 1. Number of bidders in open tenders")

#Unique bidders in the dataset
length(unique(bidders_dataset$ruc[bidders_dataset$procedure=="open"]))

#Type of tenders firms participate in
firms_type<-bidders_dataset%>%
  group_by(ruc, procedure)%>%
  summarise(total=n())%>%
  ungroup()%>%
  spread(procedure, total)%>%
  mutate(procedure=ifelse(!is.na(closed)&is.na(open), "closed",
                          ifelse(!is.na(closed)&!is.na(open), "both", "open")))
kable(table(firms_type$procedure), col.names=c("Procedure", "Number of firms"))%>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")

##Join bidders with winners
winners_full1<-winners_full%>%
  select(con, id_winner, fecha_emision, monto, ruc)

bidders_full<-bidders_dataset%>%
  left_join(winners_full1, by=c("con", "ruc"))%>%
  mutate(win=ifelse(!is.na(id_winner), 1, 0),
         type=ifelse(total_bid==1, "single bid", "other"))%>%
  group_by(con)%>%
  mutate(total_winners=sum(win))%>%
  ungroup()%>%
  mutate(monto2=monto/rate,
         amount_final=ifelse(win==1 & total_winners==1, amount_dolar,
                             ifelse(win==1 & total_winners>1 & !is.na(monto), monto2,
                                    ifelse(win==1 & total_winners>1 & is.na(monto), amount_dolar/total_winners,NA))),
         win_ruc=ifelse(win==1, ruc, NA))%>%
  group_by(con)%>%
  mutate(ruc_winners=paste0(na.omit(win_ruc), collapse = ", "),
         ruc_bidders=paste0(na.omit(ruc), collapse = ", "))%>%
  left_join(market_full, by="con")%>%
  left_join(market_final, by="con")


#General success
success<-bidders_full%>%
  filter(total_winners>0, total_bid>1, procedure=="open")%>%
  group_by(ruc)%>%
  mutate(amount=ifelse(win==1, amount_final, 0))%>%
  summarise(bids=n(),
            wins=sum(win),
            amount=sum(amount))%>%
  mutate(suc=round((wins/bids*100),1),
         suc_cat=ifelse(suc==100, "100", ifelse(suc==0, "0", "other")))


#How many bids
summary(success$bids)
success%>%
  ggplot(aes(x=bids))+
  geom_histogram()+
  theme_minimal()+
  scale_x_continuous("Number of bids")+
  scale_y_continuous("Number of firms")+
  ggtitle("Plot 2. Number of bids per firm distribution")


success%>%
  ggplot(aes(x=bids, y=(amount/1000000)))+
  geom_point()+
  theme_minimal()+
  scale_x_continuous("Number of bids")+
  scale_y_continuous("Amount of contracts won (millions of dollars)")+
ggtitle("Number of bids vs amount won")


#Success rate
summary(success$suc)
summary(success$suc[success$bids>1])

kable(round(prop.table(table(success$suc_cat[success$bids>1]))*100, 2))%>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")

success%>%
  filter(bids>1)%>%
  ggplot(aes(x=suc))+
  geom_histogram()+
  theme_minimal()+
  scale_x_continuous("Success rate")+
  scale_y_continuous("Number of firms")+
  ggtitle("Plot 4. Success rate distribution (more than 1 bid)")

kable(success%>%
        filter(bids>1)%>%
        group_by(suc_cat)%>%
        summarise(mean_tender=round(mean(bids), 1),
                  median_tender=median(bids)))%>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")


#Persistence in the market
bidders_year<-bidders_full%>%
  filter(procedure=="open")%>%
  group_by(ruc, year)%>%
  summarise(total_bids=n())%>%
  ungroup()%>%
  group_by(ruc)%>%
  mutate(years=n_distinct(year))%>%
  summarise(total_years=max(years),
            total_bids=sum(total_bids))

kable(round(prop.table(table(bidders_year$total_years))*100, 1),
      col.names = c("Year in the market","Proportion"))%>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")

single_bid<-bidders_full%>%
  group_by(con)%>%
  mutate(row=row_number())%>%
  filter(row==1, procedure=="open")%>%
  mutate(type=ifelse(total_bid==1, "single bid", "other"))
```

##Market segmentation

```{r message=FALSE, warning=FALSE, error=FALSE}
market_tenders2<-bidders_full%>%
  filter(procedure=="open")%>%
  filter(total_winners>0)%>%
  group_by(marketf)%>%
  #count number of unique tenders
  summarise(tenders=n_distinct(con))%>%
  #keep markets with more than 20 tenders
  filter(tenders>50, !is.na(marketf))

#Markets with more than 50 tenders
markets_vec2<-unique(market_tenders2$marketf)


#Success market
success_market2<-bidders_full%>%
  filter(procedure=="open", marketf %in% markets_vec2)%>%
  #keep contracts with information about the winners
  filter(total_winners>0)%>%
  group_by(marketf, ruc)%>%
  mutate(amount=ifelse(win==1, amount_final, 0))%>%
  summarise(bids=n(),
            wins=sum(win),
            amount=sum(amount),
            single_bids=sum(type=="single bid"))%>%
  mutate(suc=round((wins/bids*100),1),
         suc_cat=ifelse(suc==100, "100", ifelse(suc==0, "0", "other")),
         color=ifelse(suc==0, "#ff4040", 
                      ifelse(suc==100, "#DADD4E",
                             "#5DBCD2")))%>%
  group_by(marketf)%>%
  mutate(market_value=sum(amount))%>%
  ungroup()%>%
  mutate(cms=round((amount/market_value*100), 1))%>%
  group_by(marketf)%>%
  arrange(desc(cms), .by_group=TRUE)%>%
  mutate(rowsnum=row_number())

success_market_single2<-bidders_full%>%
  filter(procedure=="open", marketf %in% markets_vec2)%>%
  #keep contracts with information about the winners and with more than 1 bid
  filter(total_winners>0, total_bid>1)%>%
  group_by(marketf, ruc)%>%
  mutate(amount=ifelse(win==1, amount_final, 0))%>%
  summarise(bids=n(),
            wins=sum(win),
            amount=sum(amount))%>%
  mutate(suc=round((wins/bids*100),1),
         suc_cat=ifelse(suc==100, "100", ifelse(suc==0, "0", "other")),
         color=ifelse(suc==0, "#ff4040", 
                      ifelse(suc==100, "#DADD4E",
                             "#5DBCD2")))%>%
  group_by(marketf)%>%
  mutate(market_value=sum(amount))%>%
  ungroup()%>%
  mutate(cms=round((amount/market_value*100), 1))%>%
  group_by(marketf)%>%
  arrange(desc(cms), .by_group=TRUE)%>%
  mutate(rowsnum=row_number())

summary(success_market_single2$suc[success_market2$bids>1])

markets2<-success_market_single2%>%
  filter(bids>1)%>%
  group_by(marketf)%>%
  summarise(med_suc=median(suc),
            avg_suc=round(mean(suc), 2),
            perc_85=round(sum(suc>85)/n()*100,1),
            perc_zero=round(sum(suc==0)/n()*100,1))

#Plot
success_market_single2%>%
  ungroup()%>%
  mutate(marketf=ifelse(marketf=="Alquiler de instalaciones comerciales, industriales o salones", "Commercial rentals", marketf))%>%
  filter(bids>1, marketf %in% c("Commercial rentals", "Computers", "Cleaning services"))%>%
  ggplot(aes(x=suc))+
  geom_density()+
  facet_wrap(~marketf, scales="free", labeller = labeller(marketf=label_wrap_gen(width = 30)))+
  theme_minimal()+
  xlab("Success rate")+
  ylab("Density")+
  ggtitle("Success rate distribution (more than 1 bid)")


#Concentrated market structure
cms2<-bidders_full%>%
  filter(procedure=="open", marketf %in% markets_vec2)%>%
  #keep contracts with information about the winners and with more than 1 bid
  filter(total_winners>0)%>%
  group_by(marketf, ruc)%>%
  mutate(amount=ifelse(win==1, amount_final, 0))%>%
  summarise(amount=sum(amount))%>%
  group_by(marketf)%>%
  mutate(market_value=sum(amount))%>%
  ungroup()%>%
  mutate(cms=round((amount/market_value*100), 1))%>%
  group_by(marketf)%>%
  arrange(desc(cms), .by_group=TRUE)%>%
  mutate(rowsnum=row_number())


#Market stats
market_stats2<-bidders_full%>%
  filter(procedure=="open", marketf %in% markets_vec2)%>%
  filter(total_winners>0)%>%
  group_by(marketf)%>%
  mutate(amount=ifelse(win==1, amount_final, 0))%>%
  summarise(tenders=n_distinct(con),
            bidders=n_distinct(ruc),
            amount=round((sum(amount)/1000000),1),
            `bidders/tenders`=round(bidders/tenders, 1))%>%
  left_join(
    (bidders_full%>%
       filter(procedure=="open", marketf %in% markets_vec2)%>%
       filter(total_winners>0)%>%
       group_by(marketf, con)%>%
       mutate(bid=max(total_bid))%>%
       group_by(marketf)%>%
       summarise(average_bids=round(mean(bid),1),
                 median_bids=median(bid))), by="marketf")%>%
  left_join(
    (cms2%>%
       group_by(marketf)%>%
       summarise(max_csm=max(cms))), by="marketf")%>%
  left_join((single_bid%>%
               group_by(marketf)%>%
               summarise(total_tenders=n(),
                         single_bid=sum(type=="single bid"),
                         prop_single=round(single_bid/total_tenders*100,1))%>%
               select(marketf, prop_single)), by="marketf")

#Plot CMS
market_stats2%>%
  ggplot(aes(x=max_csm))+
  geom_histogram()+
  stat_bin(bins=30)+
  theme_minimal()+
  scale_x_continuous("Maximum CMS", breaks = seq(0,82,10))+
  scale_y_continuous("Number of submarkets", breaks = seq(1, 40, 1))+
  ggtitle("Distribution of max CMS (76 markets)")+
  geom_label(aes(x =42, y = 4, label = "Markets with \n high concentration"), 
             hjust = 0, 
             vjust = 0.5, 
             colour = "#555555", 
             label.size = NA, 
             family="Helvetica", 
             size = 4)
```

##Network analysis

```{r message=FALSE, warning=FALSE, error=FALSE}

library(igraph)
library(scales)
#Networks
edgelist1<-bidders_full%>%
  filter(procedure=="open", total_bid>1, total_winners>0,
         !is.na(ruc), !is.na(marketf), marketf %in% markets_vec2)%>%
  group_by(con)%>%
  mutate(total_bid=n())%>%
  filter(total_bid>1)%>%
  select(con, ruc, marketf, ruc_winners, ruc_bidders)%>%
  group_by(con, marketf, ruc_winners, ruc_bidders)%>%
  do(data.frame(t(combn(.$ruc, 2)), stringsAsFactors=FALSE))

#Create nodes
nodes1<-bidders_full%>%
  filter(procedure=="open", total_bid>1, !is.na(ruc))%>%
  group_by(con)%>%
  mutate(total_bid=n())%>%
  filter(total_bid>1)%>%
  ungroup()%>%
  distinct(ruc)

nodes_final1<-success_market2%>%
  filter(ruc %in% nodes1$ruc)

#Create networks of markets
net_list1<-list()
j<-1
set.seed(1)
for (i in markets_vec2){
  message(i)
  #filter edgelist for each market  
  m<-edgelist1%>%
    filter(marketf==i)
  #Filter nodes
  n<-nodes_final1%>%
    filter(marketf==i)
  #Create matrix
  mat<-as.matrix(m[, 5:6]) 
  #Set market name
  market_name <- i
  
  #Create network
  net<-get.adjacency(graph_from_edgelist(mat, directed=FALSE))
  g1<-graph.adjacency(net, mode="undirected", weighted=TRUE)
  net_list1[[j]]<-g1%>%
    set.vertex.attribute("win", value=n$wins[match(V(g1)$name,n$ruc)])%>%
    set.vertex.attribute("success", value=n$suc[match(V(g1)$name,n$ruc)])%>%
    set.vertex.attribute("bid", value=n$bids[match(V(g1)$name,n$ruc)])%>%
    set.vertex.attribute("amount", value=n$amount[match(V(g1)$name,n$ruc)])%>%
    set.vertex.attribute("cms", value=n$cms[match(V(g1)$name,n$ruc)])%>%
    set.vertex.attribute("color2", value=n$color[match(V(g1)$name,n$ruc)])%>%
    set.vertex.attribute("single", value=n$single_bids[match(V(g1)$name,n$ruc)])
  
  #Calculate Jaccard similarity
  sim<-similarity(net_list1[[j]], vids = V(net_list1[[j]]), mode = c("all"), loops = FALSE, method = "jaccard")
  #Add row and column names to similarity matrix
  rownames(sim)<-rownames(as.matrix(net))
  colnames(sim)<-rownames(as.matrix(net))
  #Add similarity as edge attribute
  E(net_list1[[j]])$jaccard <- sim[get.edgelist(net_list1[[j]])]
  E(net_list1[[j]])$jaccard2<-ifelse(E(net_list1[[j]])$jaccard>0.5, 1, 0) 
  E(net_list1[[j]])$w_jaccard<-E(net_list1[[j]])$jaccard*E(net_list1[[j]])$weight
  j<-j+1
  message(j)
}


#summary statistics
network<-c()
nodes<-c()
density<-c()
av_path_legth<-c()
transitivity<-c()
av_degree<-c()
cor_jaccard_intensity<-c()

j<-1
set.seed(1)
for (i in markets_vec2){
  message(i)
  message(j)
  network[j]<-i
  nodes[j]<-vcount(net_list1[[j]])
  density[j]<-round(graph.density(net_list1[[j]])*100, 3)
  av_path_legth[j]<-round(average.path.length(net_list1[[j]]), 3)
  transitivity[j]<-round(transitivity(net_list1[[j]]),3)
  av_degree[j]<-round(mean(degree(net_list1[[j]])),3)
  cor_jaccard_intensity[j]<-round(cor(E(net_list1[[j]])$jaccard, E(net_list1[[j]])$weight),3)
  j<-j+1
}

net_measures1<-data.frame(network, nodes, density, av_path_legth, transitivity,av_degree, cor_jaccard_intensity)%>%
  left_join((market_stats2%>%
               select(marketf, tenders)), by=c("network"="marketf"))

##Dataframes of edgelists interactions
library(stringi)
edgelist21<-edgelist1%>%
  mutate(from=ifelse(X1<X2, X1, X2),
         to=ifelse(from==X1, X2, X1),
         win_from=ifelse((stri_detect_fixed(ruc_winners, from)==TRUE),1,0),
         win_to=ifelse((stri_detect_fixed(ruc_winners, to)==TRUE), 1, 0))%>%
  group_by(marketf, from, to)%>%
  summarise(win_from=sum(win_from),
            win_to=sum(win_to),
            bids_edges=n())%>%
  left_join((success_market2%>%
               select(marketf, ruc, bids)), by=c("marketf", c("from"="ruc")))%>%
  left_join((success_market2%>%
               select(marketf, ruc, bids)), by=c("marketf", c("to"="ruc")))%>%
  mutate(perc_from=round(bids_edges/bids.x*100,1),
         perc_to=round(bids_edges/bids.y*100,1),
         winrate_from=round(win_from/bids_edges*100,1),
         winrate_to=round(win_to/bids_edges*100,1))


list_edges1<-list()
j<-1
for (i in markets_vec2){
  list_edges1[[j]]<-get.data.frame(net_list1[[j]])%>%
    mutate(marketf=i)
  message(i)
  j<-j+1
}
edges_info1<-do.call(rbind, list_edges1)

net_measures1<-net_measures1%>%
  left_join((edges_info1%>%
  group_by(marketf)%>%
  summarise(max_edges=max(weight))), by=c("network"="marketf"))


edges_info1<-edgelist21%>%
  left_join(edges_info1, by=c("marketf", c("from", "to")))%>%
  left_join(edges_info1, by=c("marketf", c("from"="to"), c("to"="from")))%>%
  mutate(weight=ifelse(!is.na(weight.x), weight.x, weight.y),
         jaccard=ifelse(!is.na(jaccard.x), jaccard.x, jaccard.y),
         weight_jaccard=weight*jaccard)%>%
  select(-weight.x, -weight.y, -jaccard.x, -jaccard.y)

#Table of network metrics
kable(net_measures1)%>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center")
```

## Community detection 

```{r message=FALSE, warning=FALSE, error=FALSE}
louv_list1<-list()
j<-1
for (i in markets_vec2){
  message(i)
  message(j)
  louv <- cluster_louvain(net_list1[[j]], weights = E(net_list1[[j]])$jaccard)
  louv_list1[[j]]<-data.frame(marketf=i, name=louv$names, membership=louv$membership)
  j<-j+1
}
communities1<-do.call(rbind, louv_list1)


##Assign community to each node
com_full1<-edges_info1%>%
  filter(marketf %in% markets_vec2)%>%
  left_join(communities1, by=c("marketf", c("from"="name")))%>%
  left_join(communities1, by=c("marketf", c("to"="name")))%>%
  #Keep edges of the same community
  filter(membership.x==membership.y, bids_edges>1)%>%
  group_by(marketf, membership.x)%>%
  mutate(bids_75=quantile(bids_edges,0.75))%>%
  #keep only high interaction edges
  filter(bids_edges>bids_75)%>%
  mutate(median_jac=median(jaccard),
         suspicious=ifelse(median_jac>=0.5, 1,0),
         edges=n())%>%
  filter(edges>1, suspicious==1)%>%
  select(marketf, from, to, membership.x, jaccard, median_jac, bids_edges, bids_75)


#Firms
firms1<-com_full1%>%
  select(from, to, membership.x)%>%
  gather(key=type, value=node, -marketf, -membership.x)%>%
  select(-type)%>%
  distinct()%>%
  group_by(marketf)%>%
  mutate(n_commu=n_distinct(membership.x),
         membership.x=max(membership.x))


#Assing tenders
tenders_com1<-bidders_full%>%
  filter(procedure=="open", total_bid>1, total_winners>0,
         !is.na(ruc), marketf %in% markets_vec2)%>%
  left_join(firms1, by=c("marketf", c("ruc"="node")))%>%
  mutate(com_count=ifelse(!is.na(membership.x), 1, 0),
         win_susp=ifelse(win==1 & !is.na(membership.x), 1, 0))%>%
  group_by(con)%>%
  mutate(bids_susp=sum(com_count),
         win_susp=max(win_susp),
         community=max(membership.x, na.rm = TRUE), 
         community=ifelse(community==-Inf, 0, community),
         bidders_type=ifelse(total_bid==bids_susp,"exclusive", ifelse(bids_susp>1&total_bid>1, "two or more", ifelse(bids_susp==0, "none", "only one"))),
         row=row_number())%>%
  filter(row==1)%>%
  select(-com_count, -membership.x, -row)%>%
  mutate(community_grouped=ifelse(bidders_type=="none", 0, 1))

tenders_com1$nombre_licitacion<-tolower(tenders_com1$nombre_licitacion)


#Tenders full
tenders_com1_full<-bidders_full%>%
  filter(procedure=="open", total_bid>1, total_winners>0,
         !is.na(ruc), marketf %in% markets_vec2)%>%
  left_join(firms1, by=c("marketf", c("ruc"="node")))%>%
  mutate(com_count=ifelse(!is.na(membership.x), 1, 0),
         win_susp=ifelse(win==1 & !is.na(membership.x), 1, 0))%>%
  group_by(con)%>%
  mutate(bids_susp=sum(com_count),
         win_susp=max(win_susp),
         community=max(membership.x, na.rm = TRUE), 
         community=ifelse(community==-Inf, 0, community),
         bidders_type=ifelse(total_bid==bids_susp,"exclusive", ifelse(bids_susp>1&total_bid>1, "two or more", ifelse(bids_susp==0, "none", "only one"))))%>%
  mutate(community_grouped=ifelse(bidders_type=="none", 0, 1))


#Unique communities
unique_com1<-com_full1%>%
  select(from, to, membership.x)%>%
  group_by(marketf)%>%
  mutate(n_commu=n_distinct(membership.x),
         membership.x=max(membership.x))%>%
  ungroup()%>%
  gather(key=type, value=node, -marketf, -membership.x, -n_commu)%>%
  group_by(marketf, membership.x,node, n_commu)%>%
  summarise(total=n())%>%
  ungroup()%>%
  group_by(marketf, membership.x)%>%
  summarise(total_firms=n(), 
            total_com=max(n_commu))%>%
  left_join((tenders_com1%>%
               filter(community>0)%>%
               group_by(marketf, community)%>%
               summarise(total_tenders=n(),
                         exclusive_tenders=sum(bidders_type=="exclusive"),
                         one_tender=sum(bidders_type=="only one"),
                         two_tender=sum(bidders_type=="two or more"))), by=c("marketf", c("membership.x"="community")))%>%
  mutate(tenders=exclusive_tenders+two_tender)%>%
  filter(total_tenders>50)


#Select markets and tenders
tenders_select1<-tenders_com1%>%
  filter(marketf %in% unique_com1$marketf)

#Vector of suspicious markets
f<-c(unique(unique_com1$marketf))

```


```{r message=FALSE, warning=FALSE, error=FALSE}
#Market stats and communities
market_stats2%>%
  left_join((tenders_com1%>%
               filter(procedure=="open", marketf %in% markets_vec2)%>%
               filter(total_winners>0)%>%
               group_by(marketf, year)%>%
               summarise(total_tenders=n())%>%
               group_by(marketf)%>%
               summarise(mean_tenders=mean(total_tenders))), by="marketf")%>%
  mutate(susp=ifelse(marketf %in% f, 1, 0))%>%
  ggplot(aes(y=prop_single, x=mean_tenders, color=as.factor(susp)))+
  geom_point(alpha=0.5)+
  theme_minimal()+
  ylab("Proportion of single bid tenders")+
  xlab("Average bids per year")+
  scale_color_manual(values = c("#5DBCD2", "#ff4040"), name = "", labels = c("Non suspicious", "Suspicious"))+
  ggtitle("Single bid tenders vs bidding frequency")

##Network measures and communities
net_measures1<-net_measures1%>%
  mutate(susp=ifelse(network %in% f, 1, 0))

plot_net<-function(m, n){
  print(net_measures1%>%
    ggplot(aes(x=m, fill=as.factor(susp)))+
    geom_density(alpha=.3)+theme_minimal()+
    xlab(n)+ggtitle(n)+
    scale_fill_manual(values = c("#5DBCD2", "#ff4040"), name = "", labels = c("Non suspicious", "Suspicious")))
}

plot_net(density, "Average Density")
plot_net(transitivity, "Transitivity")
plot_net(av_degree, "Average degree")
plot_net(av_path_legth, "Average path length")
plot_net(cor_jaccard_intensity, "Correlation of Jaccard similarity and bidding intensity")
plot_net(net_measures1$max_edges, "Maximum interactions")
```

##Price screens

```{r message=FALSE, warning=FALSE, error=FALSE}
library(hhi)
#Price screens
measures1<-tenders_select1%>%
  group_by(marketf, win_susp)%>%
  summarise(total=n(),
            av=mean(amount_dolar), 
            med=median(amount_dolar),
            stdev=sd(amount_dolar),
            cv=stdev/av)

#Statistical significance of price differences
for (i in f){
  message(i)
  print(wilcox.test(tenders_select1$amount_dolar[tenders_select1$marketf==i] ~ tenders_select1$win_susp[tenders_select1$marketf==i]))
}

#Plot price differences
tenders_select1%>%
  mutate(groups=ifelse(bidders_type %in% c("exclusive"), 1, 0))%>%
  ggplot(aes(x=log(amount_dolar), fill=as.factor(groups)))+
  geom_density(alpha=.3)+ggtitle("Distribution of contract value awarded by group")+theme_minimal()+
  facet_wrap(~marketf, ncol=2, scales="free", labeller = labeller(marketf=label_wrap_gen(width = 30)))+
  theme(legend.position="top")+
  xlab("Amount dollars (log scaled)")+
  scale_fill_manual(values = c("#5DBCD2", "#ff4040"), name = "", labels = c("None or one", "More than 2"))

##suspicious firms
firms_susp<-firms1%>%
  filter(marketf %in% tenders_select1$marketf)%>%
  select(marketf, node)%>%
  mutate(susp=1)

#Percentage tenders won by group
susp_winners<-tenders_select1%>%
  group_by(marketf)%>%
  summarise(total_tenders=n(),
            winns=sum(win_susp))%>%
  mutate(perc=round(winns/total_tenders*100,1))
```


#Market shares
```{r message=FALSE, warning=FALSE, error=FALSE}

#CMS for each market
cms_single<-cms2%>%
  select(marketf, ruc, cms)%>%
  rename(cms_full=cms)

markets_screens<-bidders_full%>%
  filter(con %in% tenders_select1$con, !is.na(ruc))%>%
  group_by(marketf)%>%
  mutate(total_tenders=n_distinct(con))%>%
  group_by(marketf, ruc)%>%
  mutate(amount=ifelse(win==1, amount_final, 0))%>%
  summarise(bids=n(),
            wins=sum(win),
            amount=sum(amount),
            total_tenders=max(total_tenders))%>%
  mutate(suc=round((wins/bids*100),1),
         suc_cat=ifelse(suc==100, "100", ifelse(suc==0, "0", "other")),
         market_value=sum(amount),
         cms=round((amount/market_value*100), 1),
         perc_tender=round(bids/total_tenders*100,1))%>%
  left_join(cms_single, by=c("marketf", "ruc"))%>%
  left_join(firms_susp, by=c("marketf", c("ruc"="node")))%>%
  mutate(susp=ifelse(is.na(susp), 0, susp))%>%
  left_join((bidders_info%>%
               select(id, ruc, bussi_name, legal_rep, type_prov, phone, mail, address, city, department)), by="ruc")%>%
  mutate(colorsusp=ifelse(susp==0, "#5DBCD2", "#ff4040"))


#Market screen stats
f<-c(unique(unique_com1$marketf))
for (i in f){
  message(i)
  print(i)
  print(sum(markets_screens$cms[markets_screens$marketf==i & markets_screens$susp==1]))
  print(max(markets_screens$cms[markets_screens$marketf==i & markets_screens$susp==1]))
  print((length(markets_screens$suc_cat[markets_screens$marketf==i & markets_screens$suc_cat=="0"])/
           length(markets_screens$suc_cat[markets_screens$marketf==i])*100))
}


collusive_markets<-c("Airplane travel", "Building insurance", "Cleaning services",
                     "Lab equipment", "Security guards services", "Tires",
                     "Vehicle insurance", "Vehicle repair and maintenance")
markets_screens%>%
  filter(marketf %in% collusive_markets)%>%
  ggplot(aes(x=suc, y=bids, size=cms, color=as.factor(susp)))+
  geom_point(alpha=0.5)+
  facet_wrap(~marketf, scales="fixed", labeller = labeller(marketf=label_wrap_gen(width = 30)), ncol=4)+
  theme_minimal()+
  xlab("Success rate")+
  ylab("Number of bids")+
  scale_color_manual(values = c("#5DBCD2", "#ff4040"), name = "", labels = c("Non suspicious", "Suspicious"))+
  ggtitle("Success rate vs Number of bids")

noncollu<-c("Food, beverages and tobacco", "Medical equipment")
markets_screens%>%
  filter(marketf %in% noncollu)%>%
  ggplot(aes(x=suc, y=bids, size=cms, color=as.factor(susp)))+
  geom_point(alpha=0.5)+
  facet_wrap(~marketf, scales="fixed", labeller = labeller(marketf=label_wrap_gen(width = 30)))+
  theme_minimal()+
  xlab("Success rate")+
  ylab("Number of bids")+
  scale_color_manual(values = c("#5DBCD2", "#ff4040"), name = "", labels = c("Non suspicious", "Suspicious"))+
  ggtitle("Success rate vs Number of bids")

markets_screens<-as.data.frame(markets_screens)

#HHI
hhivec<-c()
market<-c()
j<-1
for (i in f) {
  message(i)
  message(j)
  market[j]<-i
  hhivec[j]<- hhi(markets_screens[markets_screens$marketf==i,], "cms")
j<-j+1
}
hhi_df<-data.frame(marketf=market, hhi=hhivec)



markets_screens_year<-bidders_full%>%
  filter(con %in% tenders_select1$con, !is.na(ruc))%>%
  group_by(marketf, year)%>%
  mutate(total_tenders=n_distinct(con))%>%
  group_by(marketf, ruc, year)%>%
  mutate(amount=ifelse(win==1, amount_final, 0))%>%
  summarise(bids=n(),
            wins=sum(win),
            amount=sum(amount),
            total_tenders=max(total_tenders))%>%
  group_by(marketf, year)%>%
  mutate(suc=round((wins/bids*100),1),
         suc_cat=ifelse(suc==100, "100", ifelse(suc==0, "0", "other")),
         market_value=sum(amount),
         cms=round((amount/market_value*100), 1),
         perc_tender=round(bids/total_tenders*100,1))%>%
  left_join(firms_susp, by=c("marketf", c("ruc"="node")))%>%
  mutate(susp=ifelse(is.na(susp), 0, susp))

markets_screens_year<-as.data.frame(markets_screens_year)

#HHI function years
hhi_years<-function(y){
hhivec<-c()
market<-c()
j<-1
for (i in f) {
  message(i)
  market[j]<-i
  m<-markets_screens_year%>%
    filter(marketf==i, year==y)
  hhivec[j]<-hhi(m, "cms")
  j<-j+1
}
return(data.frame(marketf=market, year=rep(y, 23), hhi=hhivec))
}

hhi_yearsdf<-rbind(hhi_years(2014), hhi_years(2015), hhi_years(2016), hhi_years(2017), hhi_years(2018))

#See stability over time
hhi_stable<-hhi_yearsdf%>%
  group_by(marketf)%>%
  summarise(sd_markets=sd(hhi))

hhi_df<-hhi_df%>%
  left_join((hhi_yearsdf%>%
               group_by(marketf)%>%
               summarise(sd_hhi=sd(hhi))), by="marketf")
#plot
hhi_df%>%
  ggplot(aes(x=hhi, y=sd_hhi))+
  geom_point(alpha=0.5, size=2)+
  theme_minimal()+
  xlab("HHI")+
  ylab("Sd deviation")+
  ggtitle("Standard deviation of HHI in suspicious markets (2014-2018)")

#Success rate
markets_screens%>%
  filter(bids>1)%>%
  ggplot(aes(x=suc, fill=as.factor(susp)))+
  geom_histogram(alpha=.3)+theme_minimal()+
  ggtitle("Success rate distribution")+
  xlab("Success rate")+
  scale_fill_manual(values = c("#5DBCD2", "#ff4040"), name = "", labels = c("Non suspicious", "Suspicious"))+facet_wrap(~marketf, scales="free", ncol=4, labeller = labeller(marketf=label_wrap_gen(width = 20)))

for (i in f){
  message(i)
  print(i)
  print(wilcox.test(markets_screens$suc[markets_screens$marketf==i & markets_screens$bids>1] ~ markets_screens$susp[markets_screens$marketf==i & markets_screens$bids>1]))
}

##Special markets
library("ggsci")
special_markets<-function (x){
  m<-markets_screens$ruc[markets_screens$marketf==x & markets_screens$susp==1]
  m2<-bidders_full%>%
    filter(con %in% tenders_select1$con, !is.na(ruc), marketf==x)%>%
    group_by(year)%>%
    mutate(amount=ifelse(win==1, amount_final, 0),
           total_value=sum(amount))%>%
    filter(ruc %in% m)%>%
    group_by(year, ruc)%>%
    mutate(firm_value=sum(amount),
           cms=firm_value/total_value*100)%>%
    summarise(firm_value=max(firm_value),
              cms=max(cms))
  print(m2%>%
          ggplot()+
          geom_line(aes(x=year, y=cms, color=ruc))+
          theme_minimal()+ggtitle(x)+
          scale_color_jco())
}

special_markets("Airplane travel")
special_markets("Security guards services")

```


```{r eval=FALSE}
#Save networks to gephi format for plotting

library(rgexf)
j<-1
for (i in markets_vec2){
  gephi<-igraph.to.gexf(net_list1[[j]])
  f1 <- file(paste0(i,".gexf"))
  writeLines(gephi$graph, con = f1)
  close(f1)
  message(i)
  j<-j+1
}