---
title: "Scrapping code DNCP"
author: "Camila Salazar"
date: "8/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The datsets used for the project: *Who won the contract? An analysis of bidder networks and collusion in public procurement* were downloaded from the [DNCP website](https://www.contrataciones.gov.py/datos/api/v2/).  Heres is the code used for scrapping datasets about the tenders, tenderers, bidders, winners, products.  

The first thing to do is to download the csv files of the awards between 2014 and 2018 in this [link](https://www.contrataciones.gov.py/datos/adjudicaciones).  Save all this files in the working directory.  

In order to scrappe the information you need to [register an application](https://www.contrataciones.gov.py/datos/login) in the DNCP website to get an access token.   In the code, where it says "YOUR REQUEST TOKEN FROM THE APPLICATION", replace it with your own request token from the application. 


```{r, eval=FALSE, message=FALSE, warning=FALSE, error=FALSE}
  setwd("YOUR WORKING DIRECTORY")
#Load packages
library(httr)
library(jsonlite)
library(dplyr)
library(readr)
library(tidyr)

#Merges together the files of the awards
fls<-list.files(pattern=".csv")
file_list<-list()
  for (i in fls){
    file_list[[i]]<-data.frame(read.csv(i, stringsAsFactors = FALSE))
    message(i)
    file_list[[i]]$year<-i
    file_list[[i]]$year<-sub('.csv', "", file_list[[i]]$year)
  }
adj<-do.call(rbind, file_list)
#Filter dataset
adj<-adj%>%
  filter(X_estado%in%c("EJE", "EJEP"), year>=2014)%>%
  separate(convocante, into=c("institution", "institution2", "branch"), sep="/", remove=FALSE)%>%
  mutate(branch=ifelse((is.na(branch) & !is.na(institution) & !is.na(institution2)), institution2, branch),
         institution2=ifelse(institution2==branch, institution, institution2),
         institution=ifelse(institution2==institution,NA, institution))

#Creates a list of ids of each tender
ids<-c(adj$id)
```

### Bidders scrapping
```{r, eval=FALSE}
#Generate token
df.list <- list()
try(
for (i in ids){
  #Request token
req_token <- POST(url ="https://www.contrataciones.gov.py:443/datos/api/v2/oauth/token",
     config=add_headers(Authorization = (paste0("Basic ", "YOUR REQUEST TOKEN FROM THE APPLICATION"))))%>%
  content("text")%>%
  fromJSON(flatten=TRUE)

#Get bidders
prueba2<- GET(paste("https://www.contrataciones.gov.py:443/datos/api/v2/doc/adjudicaciones/",i,"/oferentes?show_pagination=false", sep=''), config=add_headers(Authorization = (paste0("Bearer ", req_token[2]))))

if (prueba2$status_code==404){
  next
  }

if (prueba2$status_code!=200){
  req_token <- POST(url ="https://www.contrataciones.gov.py:443/datos/api/v2/oauth/token",
     config=add_headers(Authorization = (paste0("Basic ", "YOUR REQUEST TOKEN FROM THE APPLICATION"))))%>%
    content("text")%>%
    fromJSON(flatten=TRUE)

  prueba2<- GET(paste("https://www.contrataciones.gov.py:443/datos/api/v2/doc/adjudicaciones/",i,"/oferentes?show_pagination=false", sep=''), config=add_headers(Authorization = (paste0("Bearer ", req_token[2]))))%>%
  content("text")%>%
  fromJSON(flatten=TRUE)
test<-unlist(prueba2$`@graph`$proveedor.list)
x<-length(test)/3
for (m in 1:x){
  for (j in m+x){
    for (k in j+x){
      df.list[[length(df.list)+1]] <- data.frame(con=i,
        id=test[m], razon=test[j], ruc=test[k])
      message(i)
      message(which(ids==i))
      df <- do.call(rbind, df.list)
    }}}}

else {
  prueba2<-prueba2%>%content("text")%>%
  fromJSON(flatten=TRUE)
test<-unlist(prueba2$`@graph`$proveedor.list)
x<-length(test)/3
for (m in 1:x){
  for (j in m+x){
    for (k in j+x){
      df.list[[length(df.list)+1]] <- data.frame(con=i,
        id=test[m], razon=test[j], ruc=test[k])
      message(i)
      message(which(ids==i))
      df <- do.call(rbind, df.list)
    }}}}
}, silent = TRUE)

#Save data
write.csv(df, "bidders_full_dataset.csv")
```

### Winners scraping
```{r, eval=FALSE}
##Scrape winners
#Generate token
df.list <- list()
try(
for (i in ids){
  #Request token
req_token <- POST(url ="https://www.contrataciones.gov.py:443/datos/api/v2/oauth/token",
     config=add_headers(Authorization = (paste0("Basic ", "YOUR REQUEST TOKEN FROM THE APPLICATION"))))%>%
  content("text")%>%
  fromJSON(flatten=TRUE)

#Get winners
winner <- GET(paste("https://www.contrataciones.gov.py:443/datos/api/v2/doc/adjudicaciones/",i,"/proveedores?show_pagination=false", sep=''),config=add_headers(Authorization = (paste0("Bearer ", req_token[2]))))

if (winner$status_code==404){
  next
  }

if (winner$status_code!=200){
  req_token <- POST(url ="https://www.contrataciones.gov.py:443/datos/api/v2/oauth/token",
     config=add_headers(Authorization = (paste0("Basic ", "YOUR REQUEST TOKEN FROM THE APPLICATION"))))%>%
    content("text")%>%
    fromJSON(flatten=TRUE)

  winner<- GET(paste("https://www.contrataciones.gov.py:443/datos/api/v2/doc/adjudicaciones/",i,"/proveedores?show_pagination=false", sep=''),config=add_headers(Authorization = (paste0("Bearer ", req_token[2]))))%>%
  content("text")%>%
  fromJSON(flatten=TRUE)
  
test<-unlist(winner$`@graph`$contrato.list)
x<-length(test)/10
for (m in 1:x){
  for (j in m+x){
    for (k in j+x){
      for(l in k+x){
        for(n in l+x){
          for(o in n+x*4){
            for(p in o+x){
      df.list[[length(df.list)+1]] <- data.frame(con=i,
        id_winner=test[m], codigo_contr=test[j], fecha_emision=test[k],
        monto=test[l], moneda=test[n], razon=test[o], ruc=test[p])
      message(i)
      message(which(ids==i))
      df <- do.call(rbind, df.list)
    }}}}}}}}

else {
  winner<-winner%>%content("text")%>%
  fromJSON(flatten=TRUE)
test<-unlist(winner$`@graph`$contrato.list)
x<-length(test)/10
for (m in 1:x){
  for (j in m+x){
    for (k in j+x){
      for(l in k+x){
        for(n in l+x){
          for(o in n+x*4){
            for(p in o+x){
      df.list[[length(df.list)+1]] <- data.frame(con=i,
        id_winner=test[m], codigo_contr=test[j], fecha_emision=test[k],
        monto=test[l], moneda=test[n], razon=test[o], ruc=test[p])
      message(i)
      message(which(ids==i))
      df <- do.call(rbind, df.list)
    }}}}}}}
}}, silent = TRUE)

write.csv(df, "winners_full_dataset.csv")
```

### Bidders info scraping
```{r, eval=FALSE}
#Open dataset
bidders_dataset <- read_csv("final datasets/bidders_dataset.csv", col_types = cols(X1 = col_skip()))

#unique bidders
unique_bidders<-bidders_dataset%>%
  group_by(id)%>%
  summarise(total=n())

#unique ids
ids_bid<-c(unique_bidders$id)

#Scrappe bidder info
#Generate token
df.list <- list()
try(
for (i in ids_bid){
  #Request token
req_token <- POST(url ="https://www.contrataciones.gov.py:443/datos/api/v2/oauth/token",
     config=add_headers(Authorization = (paste0("Basic ", "YOUR REQUEST TOKEN FROM THE APPLICATION"))))%>%
  content("text")%>%
  fromJSON(flatten=TRUE)

#Get bidders
bidder<- GET(paste("https://www.contrataciones.gov.py:443/datos/api/v2/doc/proveedores/",i, sep=''), config=add_headers(Authorization = (paste0("Bearer ", req_token[2]))))

if (bidder$status_code==404){
  next
  }

if (bidder$status_code!=200){
  req_token <- POST(url ="https://www.contrataciones.gov.py:443/datos/api/v2/oauth/token",
     config=add_headers(Authorization = (paste0("Basic ", "YOUR REQUEST TOKEN FROM THE APPLICATION"))))%>%
    content("text")%>%
    fromJSON(flatten=TRUE)

  bidder<- GET(paste("https://www.contrataciones.gov.py:443/datos/api/v2/doc/proveedores/",i, sep=''), config=add_headers(Authorization = (paste0("Bearer ", req_token[2]))))%>%
  content("text")%>%
  fromJSON(flatten=TRUE)
test<-unlist(bidder$`@graph`)
      df.list[[length(df.list)+1]] <- data.frame(id_bid=i,
        id=test[1], ruc=test[2], bussi_name=test[3], fantasy_name=test[4],
        legal_rep=test[5], type_prov=test[7], buss_size=test[9],
        type_activity=test[11], activity_des=test[12], phone=test[13], mail=test[14],
        web=test[15], address=test[16], city=test[17], department=test[19],
        country=test[21], lat=test[22], long=test[23])
      message(i)
      message(which(ids_bid==i))
      df <- do.call(rbind, df.list)
    }

else {
  bidder<-bidder%>%content("text")%>%
  fromJSON(flatten=TRUE)
test<-unlist(bidder$`@graph`)
      df.list[[length(df.list)+1]] <- data.frame(id_bid=i,
        id=test[1], ruc=test[2], bussi_name=test[3], fantasy_name=test[4],
        legal_rep=test[5], type_prov=test[7], buss_size=test[9],
        type_activity=test[11], activity_des=test[12], phone=test[13], mail=test[14],
        web=test[15], address=test[16], city=test[17], department=test[19],
        country=test[21], lat=test[22], long=test[23])
      message(i)
      message(which(ids_bid==i))
      df <- do.call(rbind, df.list)
    }
}, silent = TRUE)


bidunique<-bidders_info%>%
  group_by(legal_rep)%>%
  summarise(total=n())
```

###Product scrapping

```{r, eval=FALSE}

df.list <- list()
try(
  for (i in ids){
    #Request token
    req_token <- POST(url ="https://www.contrataciones.gov.py:443/datos/api/v2/oauth/token",
                      config=add_headers(Authorization = (paste0("Basic ", "YOUR REQUEST TOKEN FROM THE APPLICATION"))))%>%
      content("text")%>%
      fromJSON(flatten=TRUE)
    
    #Get submarkets
    prueba2<-GET(paste("https://www.contrataciones.gov.py:443/datos/api/v2/doc/ocds/tender/",i, sep=''), config=add_headers(Authorization = (paste0("Bearer ", req_token[2]))))
    
    if (prueba2$status_code==404){
      next
    }
    
    if (prueba2$status_code!=200){
      req_token <- POST(url ="https://www.contrataciones.gov.py:443/datos/api/v2/oauth/token",
                        config=add_headers(Authorization = (paste0("Basic ", "YOUR REQUEST TOKEN FROM THE APPLICATION"))))%>%
        content("text")%>%
        fromJSON(flatten=TRUE)
      
      prueba2<-GET(paste("https://www.contrataciones.gov.py:443/datos/api/v2/doc/ocds/tender/",i, sep=''), config=add_headers(Authorization = (paste0("Bearer ", req_token[2]))))%>%
        content("text")%>%
        fromJSON(flatten=TRUE)
      
      test<-unlist(prueba2$releases$tender.items)
      if (is.null(test)) {
        next
      } else {
        x<-length(test)/10
        if (x==1){
          df.list[[length(df.list)+1]] <- data.frame(con=i,
                                                     submarket=test["description"], id_submarket=test["classification.id"])
        } else {
          for (m in 1:x){
            df.list[[length(df.list)+1]] <- data.frame(con=i,
                                                       submarket=test[paste0("description", m)], id_submarket=test[paste0("classification.id", m)])}}
        
        message(i)
        message(which(ids_bid==i))
        df <- do.call(rbind, df.list)
      }}
    
    else {
      prueba2<-prueba2%>%content("text")%>%
        fromJSON(flatten=TRUE)
      test<-unlist(prueba2$releases$tender.items)
      if (is.null(test)) {
        next
      } else {
        x<-length(test)/10
        if (x==1){
          df.list[[length(df.list)+1]] <- data.frame(con=i,
                                                     submarket=test["description"], id_submarket=test["classification.id"])
        } else {
          for (m in 1:x){
            df.list[[length(df.list)+1]] <- data.frame(con=i,
                                                       submarket=test[paste0("description", m)], id_submarket=test[paste0("classification.id", m)])}
        }
        message(i)
        message(which(ids_bid==i))
        df <- do.call(rbind, df.list)
      }
    }
  }, silent =FALSE)
```
